A sheaf--function dictionary for algebraic tori over local fields

### 2013-10-05 shanghai.tex
Extensive reconstruction of Section 6 on finite quasicharacter sheaves.
I liked your use of alpha in Section 13 for sheaf homs, so I took
alphas out of section 6 where they were scheme homs.

\newcommand{\cdef}[1]{ {#1}\index{#1} } 
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\obj}{{\text{obj}\, }}
\newcommand{\mor}{{\text{mor}\, }}
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
\newcommand{\GN}[1]{\mathswab{#1}}
\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
\newcommand{\TT}{\underline{T}}
\newcommand{\TL}{\underline{T_L}}
\newcommand{\TTp}{\underline{T}'}
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
\newcommand{\qcs}[1]{{\mathcal{#1}}}
\newcommand{\gqcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gqcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\qcs{#1}^\dagger}
\newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
\newcommand{\QCb}{{\QC_0}}
\newcommand{\QCf}{{\QC_f}}
\newcommand{\QCiso}[1]{\QC(#1)_{/\textit{iso}}}
\newcommand{\QCbiso}[1]{\QCb(#1)_{/\text{iso}}}
\newcommand{\QCfiso}[1]{\QCf(#1)_{/\text{iso}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dualgroup}[1]{{\check{#1}}}
\newcommand{\Lang}{{\operatorname{Lang}}}
\newcommand{\image}{{\operatorname{im}}}
\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
\newcommand{\Loc}{{\operatorname{Loc}}}
\newcommand{\trFrob}[1]{t_{#1}}

@@

\begin{proposition}
Extension of scalars defines a full and faithful functor 
$B_G^* : \QCb(G) \hookrightarrow \QC(G)$.
\end{proposition}

\begin{proof}
 Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
 Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
 Then $\qcs{L}_0$ is an $\ell$-adic constructible sheaf on $G$ and
 $b_G^* \qcs{L}_0$ comes equipped with an isomorphism 
 $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$.
 Moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$  
 from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
 is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}. 
 This functor preserves local constancy, so takes local systems to local systems. 
 Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{CS.2} 
 with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
 Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
 This construction defines the functor $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
 and also shows that it is full and faithful.
\end{proof}

In general, $\QCb(G)$ is an essentially
proper subcategory of $\QC(G)$. We will identify $\QCb(G)$ with its image under $B_G^*$
and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
if it is isomorphic to some $B_G^*(\qcs{L}_0, \mu_0)$.
We will see in Corollary~\ref{cor:bounded-and-finite} that the bounded quasicharacter sheaves
are precisely those whose trace of Frobenius have bounded image.

@@

A morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny} if it is a finite, surjective
\'etale morphism of commutative group $\Fq$-schemes for which
the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
% similar nomenclature is employed in \cite{kamgarpour:09a}*{\S 2.2}.
Consider the category $C(G)$ whose objects consist of pairs $(f,\psi)$, where
\begin{itemize}
\item $f : H\to G$ is a discrete isogeny,
\item $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$.
\end{itemize}
A morphism $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\alpha,T)$, where
\begin{itemize}
\item $\alpha : H' \to H$ is a morphism of schemes such that $f' = f\circ \alpha$,
\item $T : V\to V'$ is a linear transformation equivariant for the action of
$\ker f'$ on $V'$ by $\psi'$ and the action of $\ker f'$ on $V$ by $\psi \circ \alpha$.
\[
\begin{tikzcd}
V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
V' & \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{\alpha\vert_{\ker f'}} \ker f' \arrow[hook]{r} & \arrow[swap]{u}{\alpha} H' \arrow{r}{f'} & G
\end{tikzcd}
\]
\end{itemize}
We say that $(\alpha,T)$ in $C(G)$ is a \emph{weak isomorphism} if $\alpha$ is surjective
and $T$ is an isomorphism of vector spaces.

Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.
 Morphisms in $C(G)[W^{-1}]$ are simple to describe because 
 $W$ is a left multiplicative system in the sense of
  \cite{kashiwara-schapira:CatgoriesSheaves}*{\S 7.1.7}:
a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
  \begin{equation}\label{eq:morGCf}
   \begin{tikzcd}
   (f,\psi) \arrow{r}{(\alpha_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\beta_1,U_1)} (f',\psi')
   \end{tikzcd}
  \end{equation}
 where $(\alpha',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
 and $(\beta_1,U_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism in $C(G)$. See \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.

We put a tensor category structure on $C(G)$ as follows.
Let $(f,\psi)$ and $(f',\psi')$ be objects in $C(G)$. 
Write $f\times_G f' : H\times_G H' \to G$ for the product of $f$ and $f'$
in the category of isogenies to $G$. We define an external tensor product
$\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$ and a external sum
$\psi \oplus\psi' :  \ker(f\times_G f') \to \Aut(V\oplus V')$
using the canonical isomorphism $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$.
We may thus define $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$ and
$(f,\psi)\oplus(f',\psi')\ceq (f\times_G f' ,\psi\oplus\psi')$. To define duals in $C(G)$,
let $V^\vee \ceq \Hom_\text{vec}(V,\EE)$ and $\psi^\vee : \ker f \to \Aut(V^\vee)$ be
the dual representation.  We may then set $(f,\psi)^\vee \ceq (f,\psi^\vee)$.
These operations give $C(G)$ the structure of a tensor category.
Likewise, $C(G)[W^{-1}]$ is a tensor category.

\begin{lemma}\label{lemma:finite-pullback}
Let $g : J \to G$ be a morphism of group schemes. 
Let $f_g : H\times_G J\to J$
be the pullback of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
\[
\begin{tikzcd}
V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker f_g}} \ker f_g \arrow[hook]{r}
  & \arrow[swap]{u}{g_f} H\times_G J \arrow{r}{f_g} & \arrow{u}{g} J.
\end{tikzcd}
\]
Then $(f,\psi) \mapsto (f_g,\psi_g)$
defines a monomial functor $g^* : C(G)[W^{-1}] \to C(J)[W^{-1}]$.
\end{lemma}

\begin{proof}
The key point is that pullback along $g$ takes isogenies to isogenies,
and maps over $G$ to maps over $J$, as pictured below.
\[
\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{60,between origins}}}}]
\ V \arrow{dd}{T} & \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
 & & \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
V' & \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
&& H' \arrow[pos=0.25]{rr}{f'} && G\\
 & & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
 && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} & 
\end{tikzcd}
\]
In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
were it not for the fact that pullback is defined only up to isomorphism.
In the localized categories, this ambiguity disappears. 
\end{proof}

Let $C_1(G)$ be the full, rigid monoidal subcategory of $C(G)$ consisting of objects
$(f,\psi)$ such that $\psi$ is a one-dimensional representation.

\begin{definition}
The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$,
is the rigid monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
\end{definition}

\begin{lemma}\label{lemma:finite-iso}
Each $(f,\psi)$ in $\QCf(G)$ determines a canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. 
 \end{lemma}

@@

\begin{proof}
 To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \QCf(G) \to \QCb(G)$.
 %
 We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \QCb(G)$ 
 such that $L(\alpha,T)$ is an isomorphism precisely when $(\alpha,T)$ is a weak isomorphism. 
 Factoring along $C_1(G) \to \QCb(G)$ will produce the full and faithful monoidal functor we seek.

 Now we introduce a faithful functor $L$ from $C(G)$ to the category of local systems on $G$, which we will denote by $\Loc(G)$.
 If $V$ is a $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
 For any object $(f,\psi)$ in $C(G)$, let $L(f,\psi)$ be the $\psi$-isotypic component of $f_* V_H$.
 We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$ 
 with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$ 
 and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$ 
 with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that 
 $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
 Since $L(f,\psi)$ is trivialized by $f$, it is a local system on $G$.
 For any map $(\alpha,T)$ in $C(G)$, let $L(\alpha,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined 
 %at geometric points $L(\alpha,T)_{\bar g} : L(f,\psi)_{\bar g} \to L(f',\psi')_{\bar g}$ 
 by $s \mapsto s' \ceq T\circ s\circ \alpha$. 
 This construction defines a monoidal functor $L$ from $C(G)$ to $\Loc(G)$ that
 commutes with pullback along any morphism of group schemes.

 We now show that $L$ takes weak isomorphisms in $C(G)$ to isomorphisms in $\Loc(G)$. 
 Suppose $(\beta,U) : (f,\psi)\to (f',\psi')$ is a weak isomorphism. 
 Since $U$ is an isomorphism, we may replace $V'$ with $V$ and $U$ with $\id_V$, without loss of generality. 
 Then the equivariance condition on $U$ becomes $\psi' = \psi\circ \beta$ on the finite \'etale group scheme $\ker f'$. 
 Since $f$ and $f'$ are finite \'etale, the relation $f' = f\circ \beta$ implies that $\beta$ is \'etale.  Since $\beta$ is surjective,
 it is an \'etale cover and thus admits a section $\beta' : H \to H'$. \David{Why do \'etale covers have sections?}
 This provides the inverse to $L(\beta,U) : L(f,\psi) \to L(f',\psi')$. \David{What is the inverse of $L(\beta, U)$?}

 Conversely, if $L(\alpha,T)$ is an isomorphism of local systems, 
 then $T$ must be an isomorphism of vector spaces and $\beta$ must be surjective, \David{I assume that this statement follows directly from the definition of isomorphisms of local systems?}
 whence $(\alpha,T)$ is a weak isomorphism: $W$ is saturated. \David{It's not clear to me how the claim that $W$ is saturated fits into the rest of this paragraph}

 Since $L : C(G) \to \Loc(G)$ takes weak isomorphisms to isomorphisms,
 it factors through the localization functor $C(G) \to C(G)[W^{-1}]$ 
 to define a faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$. 
 Since $W$ is saturated, the functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$ is full.

@@

For general $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
$\QCf(G)$ with its image under $B_G^* \circ L_G$, we will see in Corollary~\ref{cor:bounded-and-finite} that
a quasicharacter sheaf is finite if and only if its trace of Frobenius has finite image.

>>>>

\newcommand{\cdef}[1]{{#1}\index{#1}} 
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\obj}{{\text{obj}\, }}
\newcommand{\mor}{{\text{mor}\, }}
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
\newcommand{\GN}[1]{\mathswab{#1}}
\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
\newcommand{\TT}{\underline{T}}
\newcommand{\TL}{\underline{T_L}}
\newcommand{\TTp}{\underline{T}'}
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
\newcommand{\qcs}[1]{{\mathcal{#1}}}
\newcommand{\gqcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gqcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\qcs{#1}^\dagger}
\newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
\newcommand{\QCb}{{\QC_0}}
\newcommand{\QCf}{{\QC_f}}
\newcommand{\QCiso}[1]{\QC(#1)_{/\textit{iso}}}
\newcommand{\QCbiso}[1]{\QCb(#1)_{/\text{iso}}}
\newcommand{\QCfiso}[1]{\QCf(#1)_{/\text{iso}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dualgroup}[1]{{\check{#1}}}
\newcommand{\Lang}{{\operatorname{Lang}}}
\newcommand{\image}{{\operatorname{im}}}
\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
\newcommand{\Loc}{{\operatorname{Loc}}}
\newcommand{\trFrob}[1]{t_{#1}}

@@

\begin{proposition}\label{prop:BG}
Extension of scalars defines a full and faithful functor 
$B_G : \QCb(G) \hookrightarrow \QC(G)$.
\end{proposition}

\begin{proof}
 Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
 Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
 Then $\qcs{L}_0$ is an $\ell$-adic constructible sheaf on $G$ and
 $b_G^* \qcs{L}_0$ comes equipped with an isomorphism 
 $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$.
 Moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$  
 from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
 is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}. 
 This functor preserves local constancy, so takes local systems to local systems. 
 Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{CS.2} 
 with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
 Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
 This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
 and also shows that it is full and faithful.
\end{proof}

In general, $\QCb(G)$ is an essentially
proper subcategory of $\QC(G)$. We will identify $\QCb(G)$ with its image under $B_G$
and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
We will see in Corollary~\ref{cor:bounded-and-finite} that the bounded quasicharacter sheaves
are precisely those whose trace of Frobenius have bounded image.

@@

The definition of finite quasicharacter sheaves will require several steps, 
beginning with the localization of a category introduced here.
\Clifton{Do you think it's clear that a morphism of $\QC$-schemes is, in particular, a morphism of group schemes?}
Let us say that a morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny} if it is finite, surjective and etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f \ceq f^{-1}({\bar e)}$ is trivial.
% similar nomenclature is employed in \cite{kamgarpour:09a}*{\S 2.2}. 
Consider the category $C(G)$ whose objects consist of pairs $(f,\psi)$, where
\begin{itemize}
\item $f : H\to G$ is a discrete isogeny of $\QC$-schemes,
\item $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$.
\end{itemize}
A morphism $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(g,T)$, where
\begin{itemize}
\item $g : H' \to H$ is a morphism of schemes such that $f' = f\circ g$,
\item $T : V\to V'$ is a linear transformation, equivariant for the action of
$\ker f'$ on $V'$ by $\psi'$ and the action of $\ker f'$ on $V$ by $\psi \circ \alpha$.
\[
\begin{tikzcd}
V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
V' & \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{g\vert_{\ker f'}} \ker f' \arrow[hook]{r} & \arrow[swap]{u}{g} H' \arrow{r}{f'} & G
\end{tikzcd}
\]
\end{itemize}

We put a tensor category structure on $C(G)$ as follows.
Let $(f,\psi)$ and $(f',\psi')$ be objects in $C(G)$. 
Write $f\times_G f' : H\times_G H' \to G$ for the product of $f$ and $f'$
in the category of isogenies to $G$. We define an external tensor product
$\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$ and a external sum
$\psi \oplus\psi' :  \ker(f\times_G f') \to \Aut(V\oplus V')$
using the canonical isomorphism $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$.
We may thus define $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$ and
$(f,\psi)\oplus(f',\psi')\ceq (f\times_G f' ,\psi\oplus\psi')$. To define duals in $C(G)$,
let $V^\vee \ceq \Hom_\text{vec}(V,\EE)$ and $\psi^\vee : \ker f \to \Aut(V^\vee)$ be
the dual representation.  We may then set $(f,\psi)^\vee \ceq (f,\psi^\vee)$.
These operations give $C(G)$ the structure of a tensor category.

Now we localize $C(G)$.
Let us say that $(g,T)$ in $C(G)$ is a \emph{weak isomorphism} if $g$ is surjective
and $T$ is an isomorphism of vector spaces.
\Clifton{Should this be another lemma in this section?}
The set $W$ of weak isomorphisms in $C(G)$
is a saturated, left multiplicative system in $C(G)$ in the sense of
  \cite{kashiwara-schapira:CatgoriesSheaves}*{Defs 7.1.5, 7.1.19}.
Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at $W$.
A morphism in $C(G)[W^{-1}]$ is an equivalence class of a diagram
  \begin{equation}\label{eq:morGCf}
   \begin{tikzcd}[column sep=50]
   (f,\psi) \arrow{r}{(g_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(h_1,U_1)} (f',\psi')
   \end{tikzcd}
  \end{equation}
 where $(g',T') : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
 and $(h_1,U_1) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$; see \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
%Likewise, $C(G)[W^{-1}]$ is a tensor category.

\begin{definition}
Let $C_1(G)$ be the full, rigid monoidal subcategory of $C(G)$ consisting of objects
$(f,\psi)$ such that $\psi$ is a one-dimensional representation.
%
The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$,
is the rigid monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
\end{definition}

Having defined finite quasicharacter sheaves, 
we justify our terminology by showing $\QCf(G)$ is a full subcategory of $\QCb(G)$.
To prepare for that result, we need two lemmas.

\begin{lemma}\label{lemma:finite-pullback}
Let $g : J \to G$ be a morphism of $\QC$-schemes. 
Let $f_g : H\times_G J\to J$
be the pullback of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
\[
\begin{tikzcd}
V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker f_g}} \ker f_g \arrow[hook]{r}
  & \arrow[swap]{u}{g_f} H\times_G J \arrow{r}{f_g} & \arrow{u}{g} J.
\end{tikzcd}
\]
Then $(f,\psi) \mapsto (f_g,\psi_g)$
defines a monomial functor $g^* : C(G)[W^{-1}] \to C(J)[W^{-1}]$.
\end{lemma}

\begin{proof}
The key point is that pullback along $g$ takes discrete isogenies to discrete isogenies,
and maps over $G$ to maps over $J$, as pictured below.
\[
\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{60,between origins}}}}]
\ V \arrow{dd}{T} & \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
 & & \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
V' & \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
&& H' \arrow[pos=0.25]{rr}{f'} && G\\
 & & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
 && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} & 
\end{tikzcd}
\]
In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
were it not for the fact that pullback is defined only up to isomorphism.
In the localized categories, this ambiguity disappears. 
\end{proof}

\begin{lemma}\label{lemma:finite-iso}
Each finite quasicharacter sheaf $(f,\psi)$ in $\QCf(G)$ determines a canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. 
 \end{lemma}

@@

\begin{proof}
 To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \QCf(G) \to \QCb(G)$.

 If $V$ is a finite-dimensional $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
If $(f,\psi)$ is a finite quasicharacter on $G$ where $\psi$ is a representation of $\ker f$ on $V$, 
let $L(f,\psi)$ be the local system on $G$ given by the $\psi$-isotypic component of the local system $f_* V_H$ on $G$.
 We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$ 
 with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$ 
 and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$ 
 with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that 
 $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.

 For any map $(g,T)$ in $C(G)$, let $L(g,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined 
 by $s \mapsto s' \ceq T\circ s\circ g$. 
 This construction defines a full monoidal functor $L$ from $C(G)$ to the category $\Loc(G)$ of local systems on $G$ that
 commutes with pullback along any morphism of $\QC$-schemes,
 as defined using Lemma~\ref{lemma:finite-pullback}.
 %
 \Clifton{There's detail missing here; I might want to include some of it.}
 %
 Moreover, since $L(f,T)$ is an isomorphism of local systems
 if and only if $(f,T)$ is a weak isomorphism, 
 the full functor $L : C(G) \to \Loc(G)$ factors through the localization functor $C(G) \to C(G)[W^{-1}]$ 
 to define a full and faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$;
 see \cite{kashiwara-schapira:CatgoriesSheaves}*{Exercise 7.5}.

@@

For general $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
$\QCf(G)$ with its image under $B_G \circ L_G$, as defined in Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded}, we will see in Corollary~\ref{cor:bounded-and-finite} that
a quasicharacter sheaf is finite if and only if its trace of Frobenius has finite image.
